Something about Continuous Deductive Reasoning over Streamed RDF Data, maybe claim Soundness or some other Theoretical Quality

### 2015-06-30 content/contribution/continuous-datalog.tex
Fixes to defn of axioms/facts

\begin{definition}[Fact Instance]\label{def:continuous datalog: fact instance}
A fact instance is a combination of the signature of a fact (its
predicate $p$, subject $s$ and object $o$) and its entailment time
$t$; a fact instance is denoted ${p(s,o):t}$, and is unique.
\end{definition}

@@

	Traditionally, a set of axioms $A$ entails another set of axioms $E$ in which the existence of one fact in $E$ may be justified by many distinct subsets of $A$.
	When considering streams of facts, in which one fact may occur multiple times and be considered distinct based on its entailment time, temporal information would be lost if sets of axioms including fact instances (denoted $A_{inst}$) were to entail sets of axioms without.
	As such, where a fact would be entailed by some set of facts $A$ that are instantiated on some stream, an instance of that fact should be entailed by the set of instances of those facts present on that stream.
	Furthermore, each such justification in $A_{inst}$ for a fact entails a unique instance of that fact, such that each entailed instance has a single justification within the original set of axioms, and many instances of the entailed fact may occur in the entailed set of axioms $E_{inst}$.
	This form of entailment shall be henceforth referred to as ``instance entailment'', and shall be the norm when discussing the entailments of sets of axioms that include instances of facts.

>>>>

\begin{definition}[Fact Instance]\label{def:continuous datalog: fact instance}
A fact instance is a fact with some additional temporal annotation; it
is the combination of a fact's signature (its predicate $p$, subject $s$
and object $o$) and a timestamp $t$ that is used to record the time at
which the fact was entailed. A fact instance is denoted ${p(s,o):t}$,
and is unique.
\end{definition}

\begin{definition}[]\label{def:continuous datalog: trad}
A fact instance may be stripped of its temporal annotation using the $trad()$
\end{definition}

@@

In traditional Datalog, the set of axioms in the system consist of
rules and facts. Taken together, a set of axioms $A$ entails another
set of axioms $E$ in which the existence of one fact in $E$ may be
justified by many distinct subsets of $A$.  When considering streams
of facts, in which there may be many distinct instances of a given
fact, temporal information would be lost if sets of axioms including
fact instances (denoted $A_{inst}$) were to entail sets of axioms
containing plain facts.  As such, where a fact $f$ would be entailed
by some set of facts $A$ that are instantiated on some stream, an
instance of $f$ should be entailed by the set of instances of those
facts present on that stream.  Furthermore, each such justification in
$A_{inst}$ for a fact entails a unique instance of that fact, such
that each entailed instance has a single justification within the
original set of axioms, and many instances of the entailed fact may
occur in the entailed set of axioms $E_{inst}$.  This form of
entailment shall be henceforth referred to as ``instance entailment'',
and shall be the norm when discussing the entailments of sets of
axioms that include instances of facts.
